Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
i.e.,
added initial constraints on x_0

Furthermore, 
it is practically relevant to consider constraints on the input signal $u_{k}$, 
which we assume has given bounds $\overline{u}$ and $\underline{u}$, 
such that ${\underline{u} \leq u_{k} \leq \overline{u}},\forall k\geq 0$.  
This means that the control input saturates in view of physical constraints.

@@

Next, we describe the different phases in Fig.~\ref{fig:CEGIS-precision-increment}
(blocks 1 to 5):

@@

% \addtodo{Move as much as possible from Sec~\ref{sec:cof_verification}
% to the appendix (e.g. discussion on abstract acceleration). 
% Merge the rest in Sec~\ref{sec:cof_synth}.}

@@

%\begin{enumerate}
%% \item Calculate the abstract matrices $\mathcal{A}_t, \mathcal{B}_{t},\mathcal{B}_{n}$ for the candidate closed loop solution.
We next evaluate $\hat{X}^\# \models \phi_{safety}$. If the verification holds we have a solution, and exit the loop. Otherwise, 
we find a counterexample iteration $k$ and corresponding initial point $x_0$ for which the property does not hold, which we use to locally refine the abstraction.
When the abstraction cannot be further refined, we provide them to the {\sc abstract} phase.
\todo{we should have a better argument here.}
%\end{enumerate} 
\item If we reach the {\sc abstract} phase, it means that the candidate solution is not valid,
  in which case we must refine the abstraction used by the synthesizer.
\begin{enumerate}
\item Find the constraints that invalidate the property
  %% These are the rows of $\mat{E} \in \Psi$ that intersect/segment $\hat{X}^\#$. Transforming these rows into the eigenspace of $\mat{A}_t$, and applying backward acceleration to
 as a set of counterexamples for the eigenvalues, which we define as $\phi_\Lambda$. This is a constraint in the spectrum (\emph{ie} transfer function) of the closed loop dynamics. 
\item We use $\phi_\Lambda$ to
  further constrain the characteristic polynomial  
$z^n+\sum_{i=1}^n(a_i-k_i)z^{n-i}=\prod_{i=1}^n (z-\lambda_i) : |\lambda_i|<1 \wedge \lambda_i \models \phi_{\Lambda}$. These constraints correspond to specific iterations for which the system may be unsafe.
\item Pass the refined abstraction $\phi(K)$ with the new constraints and the list of iterations $\vec{k}$ to the {\sc synthesize} phase.
  %, as well as a counterexample plant coefficients ($P_a$) and repeat the loop again. 
\end{enumerate} 
\end{enumerate}

>>>>

Furthermore, 
it is practically relevant to consider constraints on the input signal $u_{k}$
and initial states $x_0$, 
which we assume have given bounds. %%  $\overline{u}$, $\underline{u}$
%% and $\overline{x_0}$, $\underline{x_0}$, respectively.
We refer to these constraints as $\phi_{init}$:
$$\phi_{init} = {\forall k.\underline{u} \leq u_{k} \leq \overline{u}} 
\wedge \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}$$.  
In practice, 
this means that the control input saturates in view of physical constraints.

%%%-------------------------------
%%\subsection{Digital implementation of feedback controller}
%%\label{ssec:quantizationerror}
%%%-------------------------------
%%
%%\addtodo{HERE add a figure similar to Fig. \label{fig:observersystem} to explain digital features of controller.} 
%%
%%\addtodo{[The remainder of the section needs to be updated. ]}
%%The output and measurable of the plant is being sampled by an ADC, and since the full state of the
%%plant cannot be witnessed directly, the controller software includes an observer that 
%%estimates the state of the plant (see appendix for details on how such an observer
%%is constructed). In this work, we are assuming that all the states measurements are available for the state feedback purpose, and the state observer design may be disregarded.  
%%\addtodo{[Unclear what the remainder is for: ]}
%%We further presume that there are small tolerances in the system 
%%described in the following form
%%%
%%\begin{align*}
%%\mat{A} \in \mathcal{G}_A=\mat{S}\mat{J}\mat{S}^{-1} : \mat{J} \in \mathcal{G}_J
%%\end{align*}
%%\commentib{What is S?}
%%
%%Where $\mathcal{G}_J$ is a collection of eigenvalue ranges that define the frequency response of the system.
%%We presume that the internal model of the plant is an ARMA model, modified by a
%%state transform that has no tolerances. Tolerances in the eigenvectors will manifest themselves
%%as tolerances in the canonical forms outside of the row/column of interests and complicate the 
%%evaluation. Whilst it is possible to address these with this methodology, we will focus on the case
%%above for simplicity.

% \addtodo{HERE add a figure similar to Fig. \label{fig:observersystem} to explain digital features of controller.}

% \addtodo{[The remainder of the section needs to be updated. ]}
% The output and measurable of the plant is being sampled by an ADC, and since the full state of the
% plant cannot be witnessed directly, the controller software includes an observer that 
% estimates the state of the plant (see appendix for details on how such an observer
% is constructed). In this work, we are assuming that all the states measurements are available for the state feedback purpose, and the state observer design may be disregarded.  
% \addtodo{[Unclear what the remainder is for: ]}
>>>>>>> added initial constraints on x_0

@@

Next, we describe the different phases in Fig.~\ref{fig:CEGIS-precision-increment}
(blocks 1 to 4):

@@

% \addtodo{Move as much as possible from Sec~\ref{sec:cof_verification}
% to the appendix (e.g., discussion on abstract acceleration). 
% Merge the rest in Sec~\ref{sec:cof_synth}.}

@@

%\begin{enumerate}
%% \item Calculate the abstract matrices $\mathcal{A}_t, \mathcal{B}_{t},\mathcal{B}_{n}$ for the candidate closed loop solution.
We next evaluate $\hat{X}^\# \models \phi_{safety}$. If the verification holds we have a solution, and exit the loop. Otherwise, 
we find a counterexample iteration $k$ and corresponding initial point $x_0$ for which the property does not hold, which we use to locally refine the abstraction.
When the abstraction cannot be further refined, we provide them to the {\sc abstract} phase.
\todo{we should have a better argument here.}
%\end{enumerate} 
\item If we reach the {\sc abstract} phase, it means that the candidate solution is not valid,
  in which case we must refine the abstraction used by the synthesizer.
\begin{enumerate}
\item Find the constraints that invalidate the property
  %% These are the rows of $\mat{E} \in \Psi$ that intersect/segment $\hat{X}^\#$. Transforming these rows into the eigenspace of $\mat{A}_t$, and applying backward acceleration to
 as a set of counterexamples for the eigenvalues, which we define as $\phi_\Lambda$. This is a constraint in the spectrum i.e., transfer function) of the closed loop dynamics. 
\item We use $\phi_\Lambda$ to
  further constrain the characteristic polynomial  
$z^n+\sum_{i=1}^n(a_i-k_i)z^{n-i}=\prod_{i=1}^n (z-\lambda_i) : |\lambda_i|<1 \wedge \lambda_i \models \phi_{\Lambda}$. These constraints correspond to specific iterations for which the system may be unsafe.
\item Pass the refined abstraction $\phi(K)$ with the new constraints and the list of iterations $\vec{k}$ to the {\sc synthesize} phase.
  %, as well as a counterexample plant coefficients ($P_a$) and repeat the loop again. 
\end{enumerate} 
\end{enumerate}
